A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-08-01 paper/prab.tex
add affiliation of Yves
taking out Ferrario and changing Figure to Fig.

In general, it is not possible to get the maximal performance for the lowest
  price and a trade-off decision between performance and price has to be
  reached (see Figure~\ref{fig:tradeoff}).
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade-offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.

@@

Applied to multi-objective optimization problems, genes correspond to
  design variables.
The fitness of an individual is loosely related to the value of the objective
  functions for the corresponding genes.
Figure~\ref{fig:varsel} schematically depicts the connection of the
  components introduced above.
The process starts with an initially random population of individuals, each
  individual with a unique set of genes and corresponding fitness,
  representing one location in the search space.
In a next step the population is processed by the selector
  determining the $k$ fittest individuals according to their fitness values.
While the $k$ fittest individuals are passed to the variator, the
  remaining $n-k$ individuals are eliminated from the population.
The \textsc{Variator} mates and recombines the $k$ fittest individuals to
  generate new offspring.
After evaluating the fitness of all the freshly born individuals a
  \textit{generation} cycle has completed and the process can start anew.

Since there already exist plenty of implementations of evolutionary algorithms,
  we decided to incorporate the PISA library \cite{pisa} into our
  framework.
One of the advantages of PISA is that it separates variator from selector,
  rendering the library expandable and configurable.
Implementing a variator was enough to use PISA in our framework and
  retain access to all available PISA selectors.
As shown in Figure~\ref{fig:varsel}, the selector is in charge of ordering a
  set of $d$-dimensional vectors and selecting the $k$ fittest individuals
  currently in the population.
The performance of a selector depends on the number of objectives and the
  surface of the search space.
So far, we used an NSGA-II selector \cite{dpam:02} exhibiting satisfactory
  convergence performance.

@@

The basic assumption in simulation-based optimization is that we need to
  call an expensive simulation software component present in the
  constraints or objectives.
We divide the framework in three exchangeable components, as shown in
  Figure~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \scalebox{0.85}{
  \begin{tikzpicture}[text=black]
  \input{figures/opt-framework-layout.tex}
  \end{tikzpicture}
}

@@

Every available MPI process will take up one of the three available roles (see
  Figure~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
  remaining processes are divided amongst \textsc{Worker} and
  \textsc{Optimizer} roles.
Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
  MPI processes to exploit parallelism.
As shown in Figure~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
  to coordinate all ``information requests'' between the \textsc{Optimizer}
  and the \textsc{Worker}.
An information request is a job that consists of a set of design variables
  (e.g.~the genes of an individual) and a type of information it requests
  (e.g.~function evaluation or derivative).
The \textsc{Pilot} keeps checking for idle \textsc{Worker} and assigns jobs
  in the queue to any free \textsc{Worker}.
Once the \textsc{Worker} has computed and evaluated the request its results
  are returned to the \textsc{Optimizer} that originally requested the
  information.

@@

In this paper we applied the framework to reproduce the important and well
  known Ferrario matching condition for the \textsc{250 MeV injector}, a part of PSI's
  \textsc{SwissFEL} project.
The beam size and emittance optimization was successful and emittance damping
  is observed in the accelerating cavity.
Also, the influence of the number of slices employed by the envelope tracker
  with respect to convergence was investigated.
We found that the optimal slice number is around 400 for the problem addressed
  here, producing the best trade-off between computational cost and accuracy
  of the solution of the simulation.
Similarly, the gun and beam line time step was investigated confirming the
  convergence of the results.

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.

The framework was then applied to a larger beam dynamics problem at the AWA.
Optimization of the 3D beam size and energy spread was accomplished.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
The resulting beam tune can and will be used in future TBA experiments at the AWA.
This problem also took advantage of the frameworks massively parallel capabilities by
running on 2624 processes on Bebop at LCRC.

>>>>

In general, it is not possible to get the maximal performance for the lowest
  price and a trade-off decision between performance and price has to be
  reached (see Fig.~\ref{fig:tradeoff}).
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade-offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.

@@

Applied to multi-objective optimization problems, genes correspond to
  design variables.
The fitness of an individual is loosely related to the value of the objective
  functions for the corresponding genes.
Fig.~\ref{fig:varsel} schematically depicts the connection of the
  components introduced above.
The process starts with an initially random population of individuals, each
  individual with a unique set of genes and corresponding fitness,
  representing one location in the search space.
In a next step the population is processed by the selector
  determining the $k$ fittest individuals according to their fitness values.
While the $k$ fittest individuals are passed to the variator, the
  remaining $n-k$ individuals are eliminated from the population.
The \textsc{Variator} mates and recombines the $k$ fittest individuals to
  generate new offspring.
After evaluating the fitness of all the freshly born individuals a
  \textit{generation} cycle has completed and the process can start anew.

Since there already exist plenty of implementations of evolutionary algorithms,
  we decided to incorporate the PISA library \cite{pisa} into our
  framework.
One of the advantages of PISA is that it separates variator from selector,
  rendering the library expandable and configurable.
Implementing a variator was enough to use PISA in our framework and
  retain access to all available PISA selectors.
As shown in Fig.~\ref{fig:varsel}, the selector is in charge of ordering a
  set of $d$-dimensional vectors and selecting the $k$ fittest individuals
  currently in the population.
The performance of a selector depends on the number of objectives and the
  surface of the search space.
So far, we used an NSGA-II selector \cite{dpam:02} exhibiting satisfactory
  convergence performance.

@@

The basic assumption in simulation-based optimization is that we need to
  call an expensive simulation software component present in the
  constraints or objectives.
We divide the framework in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \scalebox{0.85}{
  \begin{tikzpicture}[text=black]
  \input{figures/opt-framework-layout.tex}
  \end{tikzpicture}
}

@@

Every available MPI process will take up one of the three available roles (see
  Fig.~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
  remaining processes are divided amongst \textsc{Worker} and
  \textsc{Optimizer} roles.
Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
  MPI processes to exploit parallelism.
As shown in Fig.~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
  to coordinate all ``information requests'' between the \textsc{Optimizer}
  and the \textsc{Worker}.
An information request is a job that consists of a set of design variables
  (e.g.~the genes of an individual) and a type of information it requests
  (e.g.~function evaluation or derivative).
The \textsc{Pilot} keeps checking for idle \textsc{Worker} and assigns jobs
  in the queue to any free \textsc{Worker}.
Once the \textsc{Worker} has computed and evaluated the request its results
  are returned to the \textsc{Optimizer} that originally requested the
  information.

@@

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.
In this paper we applied the framework to a beam dynamics problem at the AWA.
Optimization of the 3D beam size and energy spread was accomplished.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
The resulting beam tune can and will be used in future TBA experiments at the AWA.
This problem also took advantage of the frameworks massively parallel capabilities by
running on 2624 processes on Bebop at LCRC.

### 2018-08-01 paper/theor-experiment.tex
taking out Ferrario and changing Figure to Fig.

In this section we present numerical results of the validation benchmark and
  discuss a proof of concept application in the domain of particle
  accelerators.

@@

To ensure that the optimizer works correctly we solved the benchmark
  problem (\ref{eqn:bench}).
To that end, we use a metric for comparing the quality of a Pareto
  front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative a chosen origin.
We visualize this for $2$ objectives in Figure~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error}.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
  computed by sampling the solution provided in~\cite{hbwh:05}.

@@

\subsection{Ferrario Matching Point}\label{ferrario}

As a verification and proof of concept we reproduce the Ferrario
  matching point discovered by Ferrario \textit{et~al.}~\cite{fcpr:00},
  by formulating the problem as a  multi-objective optimization problem.
Using the low-dimensional and fast nature of their new simulation code
  Homdyn~\cite{homdyn}, an extensive beam dynamics study was conducted.

One of the results of the study presented in \cite{fcpr:00} was the discovery
  of a novel working point.
The authors noticed that the second emittance minimum can profit from the
  additional emittance compensation in the accelerating traveling wave
  structure ensuring that the second emittance minimum occurs at a higher
  energy.
This property is attained if the beam emittance has a maximum and the root
  mean square (rms) beam size has a minimum at the entrance of the first
  accelerating traveling wave structure.
This behavior is illustrated in Figure~\ref{fig:fer_match}.

\begin{figure}
  \centering
  \input{figures/ferrario_illustrated}
  \caption{Illustration of the Ferrario matching criteria: beam emittance
  attains a maximum and rms beam size a minimum at the entrance to the first
  accelerating traveling wave structure.}
  \label{fig:fer_match}
\end{figure}

By artificially reproducing this working point as the solution of a
  multi-objective optimization problem given in equations
  (\ref{eq:swissfel:p1}) to (\ref{eq:swissfel:lastdvar}),
  we demonstrate the automation of discovering optimal beam dynamics behaviors
  given a set of desired objectives.

\begin{align}
\text{min}  \quad & \left[ \Delta \text{rms}_{x,\text{peak}} = \vert 3.0 -
\text{rms}_{x,\text{peak}} \vert, \right. \label{eq:swissfel:p1}\\
                & \Delta \varepsilon_{x,\text{peak}}  = \vert 3.0 -
                \varepsilon_{x,\text{peak}} \vert, \label{eq:swissfel:p2}\\
                & \left. \vert \text{rms}_{x, \text{peak\_pos}} -
                \varepsilon_{x,\text{peak\_pos}} \vert
                \label{eq:swissfel:p3} \right]^T\\
\text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:swissfel:firstconstr}\\
          \quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:swissfel:lastconstr}\\
          \quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:swissfel:firstdvar}\\
          \quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:swissfel:seconddvar}\\
          \quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
          \quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:swissfel:lastdvar}
\end{align}

The first two objectives minimize the distance from the position of the current
  minimum peak to the expected peak location at $3.0$\,m for transverse bunch
  size (beam waist) and emittance (see Figure~\ref{fig:fer_match}).
The third objective (\ref{eq:swissfel:p3}) adds a condition preferring
  solutions that have their emittance and rms peak locations at the same
  $s$-coordinate.
Equations (\ref{eq:swissfel:firstconstr}) and (\ref{eq:swissfel:firstdvar})
  define constraints for initial conditions for the simulation: charge,
  gun voltage and laser spot size.
Design variables given in (\ref{eq:swissfel:seconddvar}) to
  (\ref{eq:swissfel:lastdvar}) correspond to field strengths of the
  first focusing magnet, its displacement, and the phase of the gun.

In order to compute the peaks, we employed an additional Python script.
This script was called in the \textsc{OPAL}~input file, after the simulation
  finished using the \texttt{SYSTEM} functionality.
Once the peaks (in a given range) were located, the two objectives
  (\ref{eq:swissfel:p1}) and (\ref{eq:swissfel:p2}) were computed and their
  values written into corresponding files.
The custom \texttt{fromFile} functor allows us to access the values stored in
  the peak finder Python script result files
%
%\vspace{0.2cm}

\begin{flushleft}
\begin{Verbatim}[fontsize=\scriptsize]
rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
statVariableAt("rms_x-peak.dat", "var"))";
\end{Verbatim}
\end{flushleft}
\vspace{0.2cm}

\noindent
The design variables and the assembly of the multi-objective optimization problem
  can be included in the \textsc{OPAL}~input file as shown below:
%\vspace{0.2cm}

\begin{flushleft}
\begin{Verbatim}[fontsize=\scriptsize]
d1: DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
d2: DVAR, VARIABLE="FIND1_MSOL10_i", LOWERBOUND="110", UPPERBOUND="120";
d3: DVAR, VARIABLE="D_LAG_RGUN", LOWERBOUND="-0.1", UPPERBOUND="0.1";
d4: DVAR, VARIABLE="D_SOLPOS", LOWERBOUND="-0.05", UPPERBOUND="0.05";

objs:    OBJECTIVES = (rmsx, emitx);
dvars:   DVARS = (d1, d2, d3, d4);
constrs: CONSTRAINTS = ();
opt:     OPTIMIZE, OBJECTIVES=objs, DVARS=dvars,
CONSTRAINTS=constrs;
\end{Verbatim}
\end{flushleft}
\vspace{0.2cm}

%All numerical experiments in this sections were executed on the
%  \textsc{Felsim} cluster at PSI\@.
%The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
%  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
%  cores.
%The nodes are connected via Infiniband network with a total bandwidth of 16
%  GB/s.

The envelope-tracker, mentioned in the previous section, was used to evaluate
  the forward problems.
We performed a beam convergence study in order to tune the simulation input
  parameters to achieve the best trade-off between simulation accuracy and
  time to solution.
These parameters include the number of slices (\texttt{NSLICE}) used in the
  envelope-tracker simulations, simulation timestep (\texttt{DT}) and gun
  timestep (\texttt{DTGUN}).

Before the simulation can be executed a number of initial beam optics
  parameters have to be defined in an input file.
Table~\ref{tbl:et_params} shows the values of these parameters for the
  envelope-tracker.
All simulations were performed up to 12.5~m of the
  \textsc{SwissFEL} 250 MeV injector~\cite{pedr:10} beam line, with
  energies reaching  up to 120 MeV.

\begin{figure}%[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{Report/dt_scan}
  \caption{Envelope-tracker with different number of slices and simulation
    time steps.}
  \label{fig:et-dt}
\end{figure}

\begin{table}
  \begin{center}
    \caption{Initial conditions for the envelope tracker.}
    \label{tbl:et_params}
    \begin{tabular}{ll}
      \hline\noalign{\smallskip}
      name & initial value \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
        Gun voltage       & $100$ MV\\
        %Solenoid current & $110.541$ A\\
        %Laser spot size  & $290 \times 10^{-6}$ m in x and y\\
        Bunch charge      & $200$ pC\\
        %DT$_{Gun}$        & $0.06$ ps\\
        DT$_{\text{Beamline}}$  & $1.5$ ps\\
        Number of slices  & $400$ \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

The parameter that affects the performance most is the number of slices.
We scanned the range from $100$ to $1000$ slices to determine the minimal
  number of slices required for stable results using various timesteps.
The results (for 100, 400 and 800 slices) of this scan are shown in
  Figure~\ref{fig:et-dt}.
Using this data we settled for $400$ slices -- increasing the slice number
  only minimally improves convergence of the results, therefore using more
  slices is inefficient.

%\begin{figure}
   %\centering
     %\includegraphics[angle=0,width=0.8\linewidth]{Report/sliceNew}
   %\caption{Scan of the envelope-tracker slice number showing its influence
            %on the exit emittance values.}
   %\label{fig:scan_slices}
%\end{figure}

In a next step the influence of different time steps was examined.
To that end a series of optimization runs with 100, 400 and 800 slices and
  varying timestep was performed.
%Figures \ref{fig:pareto_front_1} and \ref{fig:pareto_front_21} show two Pareto
Figure~\ref{fig:pareto_front_21} shows the Pareto fronts for 400 slices
  respectively using different timesteps.
As expected, increasing the number of slices while lowering the timestep
  produces more detailed results.

%\begin{figure}
  %\centering
    %\includegraphics[width=0.9\linewidth]{Report/Run1slices100a}
  %\caption{Pareto Front for the $1000$th generation with $40$ individuals
    %using 100 slices, a simulation timestep of 5 ps and a gun timestep of 0.1
    %ps.}
  %\label{fig:pareto_front_1}
%\end{figure}

\begin{figure}%[h!]
  \centering
    \includegraphics[width=0.8\linewidth]{Report/front_plot}
  \caption{Pareto front for the $1000$th generation with $40$ individuals
    using 400 slices (interesting region magnified), a simulation timestep
    of 1.5 ps.
    The individual 3 was selected for further investigations.}
  \label{fig:pareto_front_21}
\end{figure}

\subsubsection{Optimization Results}

Each of the $40$ points on the Pareto front, shown in
  Figure~\ref{fig:pareto_front_21}, represents an optimal solution, where
  emittance and beam size values are compromised to achieve the best agreement
  with the Ferrario matching point.
We selected individual $3$ based on a comparison of the emittance and beam size
  characteristics of all solutions and by retaining the feasibility of the
  beam line optics parameters.
The design variables, emittance and beam size of the selected solution are
  shown in Table~\ref{tbl:des_vars} and Figure~\ref{fig:rmsemit}.
With the multi-objective optimization framework we attain the same working
  point as reported in~\cite{pedr:10}.

\begin{table}
  \begin{center}
    \caption{The design variables for individual $3$.}
    \label{tbl:des_vars}
    \begin{tabular}{ll}
      \hline\noalign{\smallskip}
      name & value \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
        $\sigma_{x}$          & $0.262$ mm \\
        Solenoid displacement & $28.8467$ mm \\
        Gun voltage lag       & $0.0159067$ MV\\
        Solenoid current      & $111.426$ A \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

\begin{figure}%[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms}
  \caption{Beam size and emittance of individual $3$.}
  \label{fig:rmsemit}
\end{figure}

Using the input parameters of the selected solution, we performed a stability
  analysis by varying the slice number and the time step for both the gun and
  the beam line.
Figure~\ref{fig:et-dt} shows that the exit emittance stabilizes for 400
  slices and various time steps.
No difference between $800$ and $400$ slices is visible as their minimum
  maximum extension seems to be in the same range of $0.024$ mm~mrad.

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL-t} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beam size and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{Report/iff_plot_emrms_ettt}
  \caption{Comparison 3D-tracker versus envelope-tracker in case for rms$_{x}$
    and $\varepsilon_{x}$.}
  \label{fig:et-vs-tt}
\end{figure}

%\subsection{IW2: Inverse Problem}

%In order to find cross correlations we try to solve the inverse problem
  %(15) -- (23)
%%
%\begin{align}
  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
                      %\text{m}_{x,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
                      %\text{m}_{y,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
                      %\text{m}_{z,s} \right)^2 } \\
  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
%\end{align}
%%
%We try to match the beam to measurements from the real machine by minimizing
  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
  %$s$) errors for rmx beam size in each dimensions.
%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
  %R62 describe limits of correlations between planes.
%The initial Binomial distribution (with $m = ?$) has the form
%%
%\begin{equation*}
  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
  %-\frac{y^2}{2\sigma_y^2})
  %\text{.}
%\end{equation*}
%%

%Since these correlations cannot be measured we get the real values by solving
  %the inverse problem mentioned above.

%Currently we run the simulations on a low resolution space charge grid ($8
  %\times 8 \times 8$) as a proof of concept.
%In a next step a simple Python script would be applied to iteratively rerun
  %the optimizer with increasing space-charge resolution when the limits of the
  %design variables are narrow enough (iteratively diminishing search space).
%\subsection{IW2: Inverse Problem}

%In order to find cross correlations we try to solve the inverse problem
  %(15) -- (23)
%%
%\begin{align}
  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
                      %\text{m}_{x,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
                      %\text{m}_{y,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
                      %\text{m}_{z,s} \right)^2 } \\
  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
%\end{align}
%%
%We try to match the beam to measurements from the real machine by minimizing
  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
  %$s$) errors for rmx beam size in each dimensions.
%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
  %R62 describe limits of correlations between planes.
%The initial Binomial distribution (with $m = ?$) has the form
%%
%\begin{equation*}
  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
  %-\frac{y^2}{2\sigma_y^2})
  %\text{.}
%\end{equation*}
%%

%Since these correlations cannot be measured we get the real values by solving
  %the inverse problem mentioned above.

%Currently we run the simulations on a low resolution space charge grid ($8
  %\times 8 \times 8$) as a proof of concept.
%In a next step a simple Python script would be applied to iteratively rerun
  %the optimizer with increasing space-charge resolution when the limits of the
  %design variables are narrow enough (iteratively diminishing search space). 
%\vspace{-7em}

>>>>

In this section we present numerical results of the validation benchmark and
  discuss optimization of a photoinjector operated in the space charge dominated regime.

@@

To ensure that the optimizer works correctly we solved the benchmark
  problem (\ref{eqn:bench}).
To that end, we use a metric for comparing the quality of a Pareto
  front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative a chosen origin.
We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Fig.~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error}.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
  computed by sampling the solution provided in~\cite{hbwh:05}.

@@
